New lower bounds for Schur and weak Schur numbers

### 2021-05-09 article/weakschur.tex
Modif weakschur
typographie weak schur

\noindent \underline{\textbf{Case 2:} \((x,y) \in \mathcal{T} \times \mathcal{C}\)}
\par
Given that \(f(x) = f(y)\) and by definition of \(f\), \(g(x) = g(\pi(y))\). Besides, \(g(\pi(y)) \leqslant n\) since 
\(y \in \mathcal{C}\). Distinguish between two cases according to the value of \(x + \pi(y)\).
\begin{itemize}
\item \begin{sloppypar}
	If \(x + \pi(y) \leqslant a + b\) then \(g(x + \pi(y)) = g(\pi(x + y))\) (proposition \ref{prop3}). Given that \(g\) is 
	a weakly sum-free coloring, \(g(x+\pi(y)) \neq g(x)\) since \(g(x)=g(\pi(y))\) and \(x \neq \pi(y)\) since
	\({x \leqslant b < \pi(y)}\).
	\end{sloppypar}
\item \begin{sloppypar}
	If \(x+\pi(y)> a+b\) then given that \(g\) is a WSF-template and since \({g(x) = g(\pi(y)) \leqslant n}\), 
	\({g(\pi(x+\pi(y))) \neq g(x)}\).~Given that \({g(\pi(x+\pi(y))) = g(\pi(x+y))}\) (proposition \ref{prop2}), 
	\({g(\pi(x+ y)) \neq g(x)}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(g(\pi(x+y)) \neq g(x)\). If  \(g(\pi(x+y)) \leqslant n\) then \(f(x+y) = g(\pi(x+y))\). Therefore 
\(f(x+y) \neq f(x)\) since \(g(x) = f(x)\). Otherwise, \(g(\pi(x+y)) = n + 1\) and thus \(f(x+y) > n\). In particular, 
\(f(x + y) \neq f(x)\) since \(f(x) = f(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 4:} \((x,y) \in \mathcal{C}^2\)}
\par
By definition of \(f\) and since \(f(x)=f(y)\), \(g(\pi(x)) = g(\pi(y))\). Dsistinguish between two cases according 
to the value of \(\pi(x)+\pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \leqslant q\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(g(\pi(x + y) \neq g(\pi(x))\) since 
	\(g\) is sum-free for \(x>b\)
\item \begin{sloppypar} 
	If \(\pi(x)+\pi(y)>q\) then given that \(g\) is a WSF-template, \({g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x))}\) since 
	\({g(\pi(x)) = g(\pi(y))}\). Besides,  \({g(\pi(\pi(x)+\pi(y))) = g(\pi(x + y))}\) (proposition \ref{prop4}). Hence \({g(\pi(x + y)) 
	\neq  g(\pi(x))}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(g(\pi(x+y)) \neq g(x)\). If  \(g(\pi(x+y)) \leqslant n\) then \(f(x+y) = g(\pi(x+y))\). Therefore 
\(f(x+y) \neq f(x)\) since \(g(x) = f(x)\). Otherwise, \(g(\pi(x+y)) = n + 1\) and thus \(f(x+y) > n\). In particular, 
\(f(x + y) \neq f(x)\) since \(f(x) = f(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 6:} \((x,y) \in \mathcal{R}^2\)}
\par
In particular \(g(\pi(x)) = g(\pi(y))=n + 1\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\) 
	(proposition \ref{prop7}). By definition of \(f\) and since \(f(x) = f(y)\), \(h(\lambda(x)) = h(\lambda(y))\).
	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x)\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
	then \(f(x + y) = n + h(\lambda(x + y))\). And \(f(x) = n + h(\lambda(x))\). Therefore, \(f(x + y)  \neq f(x)\). 
	Otherwise \(f(x+y) \leqslant n < f(x)\). In particular \(f(x + y) \neq f(x)\).
\item If \(\pi(x)+\pi(y)>2a+b\) then \(g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x)) = n + 1\) since \(g\) is a \(b\)-WSF template and 
	\(g(\pi(x)) = g(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(g(\pi(x+y)) \neq n + 1\).
\item \begin{sloppypar}
	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(g_{| [\![b, a + b ]\!]}\) is 
	sum-free, \({g(\pi(x) + \pi(y)) \neq g(\pi(x)) = n + 1}\). That is \({g(\pi(x + y)) \neq n + 1}\) (proposition \ref{prop1}).
	\end{sloppypar}
\end{itemize}
\par
In both of the last two cases, \({g(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(f(x+y) < n \leqslant f(x)\). 
In particular, \(f(x + y) \neq f(x)\). \\
\end{proof}

>>>>

\noindent \underline{\textbf{Case 2:} \((x,y) \in \mathcal{T} \times \mathcal{C}\)}
\par
Given that \(f(x) = f(y)\) and by definition of \(f\), \(g(x) = g(\pi(y))\). Besides, \(g(\pi(y)) \leqslant n\) since 
\(y \in \mathcal{C}\). Distinguish between two cases according to the value of \(x + \pi(y)\).
\begin{itemize}
\item \begin{sloppypar}
	If \(x + \pi(y) \leqslant a + b\) then \(g(x + \pi(y)) = g(\pi(x + y))\) (proposition \ref{prop3}). Given that \(g\) is 
	a weakly sum-free coloring, \(g(x+\pi(y)) \neq g(x)\) since \(g(x)=g(\pi(y))\) and \(x \neq \pi(y)\) since
	\({x \leqslant b < \pi(y)}\).
	\end{sloppypar}
\item \begin{sloppypar}
	If \(x+\pi(y)> a+b\) then given that \(g\) is a WSF-template and since \({g(x) = g(\pi(y)) \leqslant n}\), 
	\({g(\pi(x+\pi(y))) \neq g(x)}\).~Furthermore \({g(\pi(x+\pi(y))) = g(\pi(x+y))}\) (proposition \ref{prop2}), such that 
	\({g(\pi(x+ y)) \neq g(x)}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(g(\pi(x+y)) \neq g(x)\). If  \(g(\pi(x+y)) \leqslant n\) then \(f(x+y) = g(\pi(x+y))\). Therefore 
\(f(x+y) \neq f(x)\) since \(g(x) = f(x)\). Otherwise, \(g(\pi(x+y)) = n + 1\) and thus \(f(x+y) > n\). In particular, 
\(f(x + y) \neq f(x)\) since \(f(x) = f(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 4:} \((x,y) \in \mathcal{C}^2\)}
\par
By definition of \(f\) and since \(f(x)=f(y)\), \(g(\pi(x)) = g(\pi(y))\). Distinguish between two cases according 
to the value of \(\pi(x)+\pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \leqslant a+b\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(g(\pi(x + y)) \neq g(\pi(x))\) since 
	\(g\) is sum-free for \(x>b\)
\item \begin{sloppypar} 
	If \(\pi(x)+\pi(y)>a+b\) then given that \(g\) is a WSF-template, \({g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x))}\) since 
	\({g(\pi(x)) = g(\pi(y))}\). Besides,  \({g(\pi(\pi(x)+\pi(y))) = g(\pi(x + y))}\) (proposition \ref{prop4}). Hence \({g(\pi(x + y)) 
	\neq  g(\pi(x))}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(g(\pi(x+y)) \neq g(x)\). If  \(g(\pi(x+y)) \leqslant n\) then \(f(x+y) = g(\pi(x+y))\). Therefore 
\(f(x+y) \neq f(x)\) since \(g(x) = f(x)\). Otherwise, \(g(\pi(x+y)) = n + 1\) and thus \(f(x+y) > n\). In particular, 
\(f(x + y) \neq f(x)\) since \(f(x) = f(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 6:} \((x,y) \in \mathcal{R}^2\)}
\par
In particular \(g(\pi(x)) = g(\pi(y))=n + 1\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\) 
	(proposition \ref{prop7}). By definition of \(f\) and since \(f(x) = f(y)\), \(h(\lambda(x)) = h(\lambda(y))\).
	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
	then \(f(x + y) = n + h(\lambda(x + y))\). And \(f(x) = n + h(\lambda(x))\). Therefore, \(f(x + y)  \neq f(x)\). 
	Otherwise \(f(x+y) \leqslant n < f(x)\). In particular \(f(x + y) \neq f(x)\).
\item If \(\pi(x)+\pi(y)>2a+b\) then \(g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x)) = n + 1\) since \(g\) is a \(b\)-WSF template and 
	\(g(\pi(x)) = g(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(g(\pi(x+y)) \neq n + 1\).
\item \begin{sloppypar}
	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(g_{| [\![b, a + b ]\!]}\) is 
	sum-free, \({g(\pi(x) + \pi(y)) \neq g(\pi(x)) = n + 1}\). That is \({g(\pi(x + y)) \neq n + 1}\) (proposition \ref{prop1}).
	\end{sloppypar}
\end{itemize}
\par
In both of the last two cases, \({g(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(f(x+y) < n \leqslant f(x)\). 
In particular, \(f(x + y) \neq f(x)\). \\
\end{proof}
